---
title: "Simulated traits"
author: "Frederick Boehm"
date: "9/10/2019"
output: html_document
---

## Overview

Is the null distribution of the pleiotropy test statistic a mixture of two chi-squared distributions?

Let's simulate traits for DO mice under the null pleiotropy hypothesis. We'll then do the two-dimensional scans and determine the empirical null distribution of pleiotropy test statistics. For now, all traits will be simulated with the same covariance matrix.

## Get the Attie DO data

```{r saveRDS}
if (!file.exists(here::here("data", "derived_data", "genoprobs.rds"))){
  myurl <- "https://datadryad.org/bitstream/handle/10255/dryad.166774/Attie_DO378_eQTL_viewer_v1.Rdata?sequence=2"
  download.file(myurl,
              destfile = here::here("data", "raw_data", "Attie_DO378_eQTL_viewer_v1.Rdata")
              )
  load(here::here("data", "raw_data", "Attie_DO378_eQTL_viewer_v1.Rdata"))
  saveRDS(dataset.islet.rnaseq$lod.peaks, here::here("data", "derived_data", "lod_peaks.rds"))
  saveRDS(dataset.islet.rnaseq$annots, here::here("data", "derived_data", "annots.rds"))
  saveRDS(dataset.islet.rnaseq$expr, here::here("data", "derived_data", "expr.rds"))
  saveRDS(K, here::here("data", "derived_data", "kinship.rds"))
  saveRDS(map, here::here("data", "derived_data", "map.rds"))
  saveRDS(genoprobs, here::here("data", "derived_data", "genoprobs.rds"))
  saveRDS(dataset.islet.rnaseq$covar, here::here("data", "derived_data", "covar.rds"))
}
```

```{r readRDS}
lod_peaks <- readRDS(here::here("data", "derived_data", "lod_peaks.rds"))
annots <- readRDS(here::here("data", "derived_data", "annots.rds"))
expr <- readRDS(here::here("data", "derived_data", "expr.rds"))
probs <- readRDS(here::here("data", "derived_data", "genoprobs.rds"))
K <- readRDS(here::here("data", "derived_data", "kinship.rds"))
covar <- readRDS(here::here("data", "derived_data", "covar.rds"))
map <- readRDS(here::here("data", "derived_data", "map.rds"))
```

## Simulate traits from Chr 1

```{r load-qtl2pleio}
library(qtl2pleio)
library(qtl2)
library(tidyverse)
```

```{r sims}
K2 <- matrix(nrow = 500, ncol = 500, data = 0) %>%
  (function(x) {rownames(x) <- rownames(K$`1`); colnames(x) <- colnames(K$`1`); x})
set.seed(2019-09-10)
out <- list()
for (i in 1:1000){
  tr <- sim1(X = gemma2::stagger_mats(genoprobs$`1`[ , , 1000], genoprobs$`1`[ , , 1000]),
     B = matrix(data = rep(c(1, -1, 1, -1), each = 4),
                nrow = 8, 
                byrow = FALSE),
     Vg = diag(2), 
     Ve = diag(2), 
     kinship = K2 # assume unrelated subjects
  )
  tr_mat <- matrix(data = tr, byrow = FALSE, ncol = 2)
  # add rownames and colnames
  rownames(tr_mat) <- rownames(genoprobs$`1`)
  colnames(tr_mat) <- paste0("tr", c(1, 2))
  out[[i]] <- tr_mat
}
```







```{r scan_pvl}
sp_out <- lapply(FUN = function(x) {
  qtl2pleio::scan_pvl(probs = probs$`1`,
                    pheno = x[1:100, ], 
                    kinship = K$`1`,
                    start_snp = 900, 
                    n_snp = 200)},
  X = out)
```

```{r}
sp_out %>%
  calc_profile_lods() %>%
  add_pmap(pmap = map$`1`) %>%
  ggplot() + geom_line(aes(y = profile_lod, x = marker_position, colour = trait))
```

```{r calc_lrt}
lods <- sp_out %>%
  purrr::map(.f = calc_profile_lods) %>%
  purrr::map(.f = dplyr::filter, profile_lod == max(profile_lod)) %>%
  purrr::map(.f = dplyr::select, profile_lod) %>%
  purrr::map_dbl(.f = function(x)x[[1]][1])
hist(lods)
```

```{r chisq-1-2-mixture}
mix_prob <- 0.5
rout <- numeric(length = 1000L)
for (i in seq_along(rout)){
  if (rbinom(n = 1, size = 1, prob = mix_prob)) {
    rout[i] <- rchisq(n = 1, df = 1)
    } else {
      rout[i] <- rchisq(n = 1, df = 2)
      }
}
hist(rout)
```

```{r qq}
qqplot(rout, lods)
```